\textbf{COMP0085 Summative Assignment}

### 2022-12-29 submission.tex
update eta definition to use b
fix loopy bp derivation

@@

\[\mathcal{M}_{j \rightarrow i}(s_i) \propto \exp\left(\log\left(\frac{\theta_{ji}}{1-\theta_{ji}} \right) s_i\right)\]

@@

@@

\[\eta_{j, \neg s_i} =  \log \left(\frac{\lambda_j}{1-\lambda_j}\right) + \sum_{k\in ne(i), k\neq i}^{K} \log\left(\frac{\theta_{ki}}{1-\theta_{ki}} \right)\]

Note that $\tilde{g}_{ij}(s_i, s_j)$ was chosen as the product of two Bernoulli distributions, updates to this site approximation involves updating to the natural parameters $\theta_i$ and $\theta_j$, the means of $s_i$ and $s_j$ respectively.

@@

\[\log \tilde{g}_{ij}(s_i, s_j)q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j) \propto \log \left(\frac{\theta_{ji}}{1-\theta_{ji}} \right) s_i + \log \left(\frac{\theta_{ij}}{1-\theta_{ij}} \right) s_j + \eta_{i, \neg s_j} s_i + \eta_{j, \neg s_i} s_j\]

@@

\[\log \tilde{g}_{ij}(s_i, s_j) q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j) \propto \log \left(\frac{\theta_{ji}}{1-\theta_{ji}} + \eta_{i, \neg s_j} \right) s_i + \log \left(\frac{\theta_{ij}}{1-\theta_{ij}} + \eta_{j, \neg s_i} \right) s_j \]

@@

\[\mathbb{E}_{s_i}\left[\sum_{s_j \in \{0, 1\}}\tilde{g}_{ij}(s_i, s_j) q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j)\right] = \frac{1}{1+\exp{\left(-\left(\theta_{ji} + \eta_{i, \neg s_j} \right)}\right)}\]

@@

\[\mathbb{E}_{s_j}\left[\sum_{s_i \in \{0, 1\}}\tilde{g}_{ij}(s_i, s_j) q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j)\right] = \frac{1}{1+\exp{\left(-\left(\theta_{ij} + \eta_{j, \neg s_i} \right)}\right)}\]

@@

\[\frac{1}{1+\exp{\left(-\left(\theta_{ji} + \eta_{i, \neg s_j} \right)}\right)}} = \frac{\exp\left(\eta_{i, \neg s_j}\right)\left(\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1\right)  }{\left[\exp\left(\eta_{i, \neg s_j}\right)\left(\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1\right)  \right]+\left[\exp\left( \eta_{j, \neg s_i}\right) +  1\right]}\]

\[\exp\left( \eta_{j, \neg s_i}\right) +  1=\exp{\left(-\left(\theta_{ji} + \eta_{i, \neg s_j} \right)}\right)}\exp\left(\eta_{i, \neg s_j}\right)\left(\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1\right)\]

\[\frac{\exp\left( \eta_{j, \neg s_i}\right) +  1}{ \exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1} =\exp{\left(-\theta_{ji}\right)}\]

\[\theta_{ji} = \log \left( \frac{1+\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right)}{1+\exp\left( \eta_{j, \neg s_i}\right)} \right)\]

@@

\[\theta_{ij} = \log \left( \frac{1+\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right)}{1+\exp\left( \eta_{i, \neg s_j}\right)} \right)\]

>>>>

we can define $\xi_{ji} = \log \left(\frac{\theta_{ji}}{1-\theta_{ji}} \right)$ and $\xi_{ij} = \log \left(\frac{\theta_{ij}}{1-\theta_{ij}} \right)$:

\[\log \tilde{g}_{ij}(s_i, s_j) \propto \xi_{ji} s_i + \xi_{ij} s_j\]

@@

\[\mathcal{M}_{j \rightarrow i}(s_i) \propto \exp\left(\xi_{ji} s_i\right)\]

@@

Knowing $\log \left(\frac{\lambda_i}{1-\lambda_i} \right)s_i = b_i s_i$ and $\xi_{kj} = \log\left(\frac{\theta_{kj}}{1-\theta_{kj}} \right)$:

\[\eta_{i, \neg s_j} =  b_i + \sum_{k\in ne(j), k\neq j}^{K} \xi_{kj}\]

@@

\[\eta_{j, \neg s_i} =  b_j + \sum_{k\in ne(i), k\neq i}^{K} \xi_{ki}\]

Note that $\tilde{g}_{ij}(s_i, s_j)$ was chosen as the product of two Bernoulli distributions, updates to this site approximation involves updating the  parameters $\xi_{ij}$ and $\xi_{ji}$, for $s_i$ and $s_j$ respectively.

@@

\[\log \tilde{g}_{ij}(s_i, s_j)q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j) \propto \xi_{ji} s_i + \xi_{ij} s_j + \eta_{i, \neg s_j} s_i + \eta_{j, \neg s_i} s_j\]

@@

\[\log \tilde{g}_{ij}(s_i, s_j) q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j) \propto \left(\xi_{ji}+ \eta_{i, \neg s_j} \right) s_i + \left(\xi_{ij} + \eta_{j, \neg s_i} \right) s_j \]

@@

\[\mathbb{E}_{s_i}\left[\sum_{s_j \in \{0, 1\}}\tilde{g}_{ij}(s_i, s_j) q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j)\right] = \frac{1}{1+\exp{\left(-\left(\xi_{ji} + \eta_{i, \neg s_j} \right)}\right)}\]

@@

\[\mathbb{E}_{s_j}\left[\sum_{s_i \in \{0, 1\}}\tilde{g}_{ij}(s_i, s_j) q_{\neg \tilde{g}_{ij}(s_i, s_j)}(s_i, s_j)\right] = \frac{1}{1+\exp{\left(-\left(\xi_{ij} + \eta_{j, \neg s_i} \right)}\right)}\]

@@

\[\frac{1}{1+\exp{\left(-\left(\xi_{ji} + \eta_{i, \neg s_j} \right)}\right)}} = \frac{\exp\left(\eta_{i, \neg s_j}\right)\left(\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1\right)  }{\left[\exp\left(\eta_{i, \neg s_j}\right)\left(\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1\right)  \right]+\left[\exp\left( \eta_{j, \neg s_i}\right) +  1\right]}\]

\[\exp\left( \eta_{j, \neg s_i}\right) +  1=\exp{\left(-\left(\xi_{ji} + \eta_{i, \neg s_j} \right)}\right)}\exp\left(\eta_{i, \neg s_j}\right)\left(\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1\right)\]

\[\frac{\exp\left( \eta_{j, \neg s_i}\right) +  1}{ \exp\left( W_{ij}  + \eta_{j, \neg s_i}\right) + 1} =\exp{\left(-\xi_{ji}\right)}\]

Our parameter update:

\[\xi_{ji} = \log \left( \frac{1+\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right)}{1+\exp\left( \eta_{j, \neg s_i}\right)} \right)\]

@@

\[\xi_{ij} = \log \left( \frac{1+\exp\left( W_{ij}  + \eta_{j, \neg s_i}\right)}{1+\exp\left( \eta_{i, \neg s_j}\right)} \right)\]
